Check Coverage

### 2019-07-18 analysis/merge_data.Rmd
Rename
Calculate FD metrics for each year and time point.

```{r}
library(tidyverse)
```

@@

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  #bind_rows() %>%
  filter(study_id %in% coverage$study_id)
```

>>>>

```{r}
library(tidyverse)
library(FD)
```

@@

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  filter(study_id %in% coverage$study_id)
```

```{r}
usethis::use_data(biotime_traits)
```

Get FD metrics for each study 
```{r}
load(here::here("data", "biotime_traits.rda"))

get_fd <- function(data){
  species_mat <- data %>%
    select(year, id) %>% 
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

  years <- data %>% 
    select(year) %>%
    distinct() %>%
    arrange(year)

  trait_mat <- data %>%
    select(id, diet_inv, diet_vend, diet_vect, diet_vfish, diet_vunk, diet_scav, diet_fruit, 
           diet_nect, diet_seed, diet_planto, diet_certainty, forstrat_watbelowsurf,
           forstrat_wataroundsurf, forstrat_ground, forstrat_understory, forstrat_midhigh,
           forstrat_canopy, forstrat_aerial, pelagicspecialist, forstrat_speclevel, nocturnal, 
           bodymass_value, bodymass_speclevel, forstrat_value, activity_nocturnal, activity_crepuscular, 
           activity_diurnal, Fos, Ter, Aqu, Arb, Leaves, Flowers, Seeds, Fruits, Arthro, Vert, 
           Diu, Noc, Crepu, Wet_warm, Wet_cold, Dry_warm, Dry_cold, Body_mass_g, Age_at_maturity_min_y, 
           Age_at_maturity_max_y, Body_size_mm, Size_at_maturity_min_mm, Size_at_maturity_max_mm, 
           Longevity_max_y , Litter_size_min_n, Litter_size_max_n, Reproductive_output_y, 
           Offspring_size_min_mm, Offspring_size_max_mm, Dir, Lar, Viv, OBS 
    ) %>%
    distinct() %>%
    select_if(~ length(unique(.)) > 1) %>% #remove columns that have the same value for all columns
    mutate_at(vars(-id), list(~scales::rescale(.,to=c(0, 1)))) %>% #rescale variables
    arrange(id) %>%
    column_to_rownames("id")

  as.tibble(dbFD(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .)
}

get_fd_safe <- possibly(get_fd, NA)

test_data <- biotime_traits %>% 
  filter(study_id %in% c(39, 46, 47, 51)) %>%
  group_by(study_id) %>%
  nest() %>%
  mutate(metrics = map(data, ~get_fd_safe(.x))) %>%
  filter(!is.na(metrics)) %>%
  select(-data) %>%
  unnest()
```
